Avancement du stage

### 2025-05-12 presentation.qmd
Mise à jour présentation

```{python}
display(HTML(f"Δ (AROME - Stations) : {me:+.1f} jours ({percent*100:.1f}%)"))
```

@@

```{python}
display(HTML(f"Δ (AROME - Stations) de {config["years"]["min"]} à {year_display_max} : {me_1959:+.3f} mm/j ({percent_1959*100:.1f}%)"))
display(HTML(f"Δ (AROME - Stations) de {year_display_min} à {year_display_max} : {me_2000:+.3f} mm/j ({percent_2000*100:.1f}%)"))
```

@@

```{python}
display(HTML(f"Δ (AROME - Stations) : {me:+.3f} mm/h ({percent*100:.1f}%)"))
```

@@

display(HTML(f"Δ (AROME - Stations) de {config["years"]["min"]} à {year_display_max} : {me_1959:+.3f} mm/j ({percent_1959*100:.1f}%)"))
display(HTML(f"Δ (AROME - Stations) de {year_display_min} à {year_display_max} : {me_2000:+.3f} mm/j ({percent_2000*100:.1f}%)"))
```

@@

    display(HTML(f"Δ (AROME - Stations) : {me:+.3f} mm/h ({percent*100:.1f}%)"))

>>>>

```{python}
display(HTML(f"Δ (AROME - Stations) : {me:+.1f} jours ({percent*100:+.1f}%)"))
```

@@

```{python}
display(HTML(f"Δ (AROME - Stations) de {config["years"]["min"]} à {year_display_max} : {me_1959:+.3f} mm/j ({percent_1959*100:+.1f}%)"))
display(HTML(f"Δ (AROME - Stations) de {year_display_min} à {year_display_max} : {me_2000:+.3f} mm/j ({percent_2000*100:+.1f}%)"))
```

@@

```{python}
display(HTML(f"Δ (AROME - Stations) : {me:+.3f} mm/h ({percent*100:+.1f}%)"))
```

@@

display(HTML(f"Δ (AROME - Stations) de {config["years"]["min"]} à {year_display_max} : {me_1959:+.3f} mm/j ({percent_1959*100:+.1f}%)"))
display(HTML(f"Δ (AROME - Stations) de {year_display_min} à {year_display_max} : {me_2000:+.3f} mm/j ({percent_2000*100:+.1f}%)"))
```

@@

    display(HTML(f"Δ (AROME - Stations) : {me:+.3f} mm/h ({percent*100:+.1f}%)"))
